\textsf{Are large language models superhuman chemists?}

### 2024-03-25 src/tex/ms.tex
significantly -> notably
grammar of combustion questions

Our findings also highlight the nuanced tradeoff between breadth and depth of evaluation frameworks. 
The analysis of model performance on different topics shows that the performance of models varies widely across topics. 
But even within a topic, the performance of models can vary significantly depending on the type of question and the reasoning required to answer it.

@@

\subparagraph{Combustion engineering}
\variable{output/question_count_per_dir/json_file_counts_combustion_engineering.txt} question are based on master student examination papers at the University of Magdeburg (Germany). 
They explore topics related to combustion processes and engineering principles.

>>>>

Our findings also highlight the nuanced tradeoff between breadth and depth of evaluation frameworks. 
The analysis of model performance on different topics shows that the performance of models varies widely across topics. 
But even within a topic, the performance of models can vary notably depending on the type of question and the reasoning required to answer it.

@@

\subparagraph{Combustion engineering}
\variable{output/question_count_per_dir/json_file_counts_combustion_engineering.txt} question is based on master student examination papers at the University of Magdeburg (Germany). It explores topics related to combustion processes and engineering principles.
